Making all equalities equal

### 2021-12-18 paper.lagda.tex
changed unicode character

private variable
  ℓ ℓ′ : Level
  A : Set ℓ
\end{code}

@@

\begin{code}
module FunExt {A : Set ℓ} {B : Set ℓ′} where
  open Martin-Löf

@@

\begin{code}
module CubicalResults {A : Set ℓ} {B : Set ℓ′} where
  open import Cubical.Core.Primitives

@@

module _ {ℓ} {A : Set ℓ′} where
  ≣-Type = A → A → Set ℓ
  private
    ℓ₁ = ℓ-max ℓ′ ℓ

@@

\begin{code}
liftIso : {A : Type ℓ} {B : Type ℓ′}
  → Iso {ℓ} {ℓ′} A B → Iso {ℓ-max ℓ ℓ′} {ℓ-max ℓ ℓ′} A B
liftIso f = iso fun inv
  (λ x i → rightInv x i) (λ x i → leftInv x i)
\end{code}

>>>>

private variable
  ℓ ℓ' : Level
  A : Set ℓ
\end{code}

@@

\begin{code}
module FunExt {A : Set ℓ} {B : Set ℓ'} where
  open Martin-Löf

@@

\begin{code}
module CubicalResults {A : Set ℓ} {B : Set ℓ'} where
  open import Cubical.Core.Primitives

@@

module _ {ℓ} {A : Set ℓ'} where
  ≣-Type = A → A → Set ℓ
  private
    ℓ₁ = ℓ-max ℓ' ℓ

@@

\begin{code}
liftIso : {A : Type ℓ} {B : Type ℓ'}
  → Iso {ℓ} {ℓ'} A B → Iso {ℓ-max ℓ ℓ'} {ℓ-max ℓ ℓ'} A B
liftIso f = iso fun inv
  (λ x i → rightInv x i) (λ x i → leftInv x i)
\end{code}
